A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex

\begin{table}[h!]
\centering
\begin{tabular}{|m{1em} |m{14em} |m{14em}|} 
 \hline
  & PCA & Linear Regression \\ [0.5ex] 
 \hline
 1 & Determines the best vector (or set of vectors) which compresses the data points by minimizing the orthogonal distance to the points & Approximates the best fit line for the points by minimizing the error \\
 \hline
 2 & Essentially, it forms a projection of the original points onto the new vector space & Predicts $y$ from $x$ through a function $f(x_1,x_2,....,x_n) = y$ \\
 \hline
 3 & Not used for predictions, as original feature space (\ie $x_1$ and $x_2$) give way to a new reduced dimension. Cordinates $x_1, x_2,...,x_n$ give way to $z_1,....,z_k$ where $k \leq n$ & \\[1ex]
 \hline
\end{tabular}
\caption{Table comparing PCA with Linear Regression}
\label{table:pca_vs_linreg}
\end{table}

>>>>

\begin{table}[h!]
\centering
\begin{tabular}{|m{1em} |m{14em} |m{14em}|} 
 \hline
  & \begin{center}{\bf PCA}\end{center} & \begin{center}{\bf Linear Regression}\end{center} \\ [0.5ex] 
 \hline
 1 & Determines the best vector (or set of vectors) which compresses the data points by minimizing the orthogonal distance to the points & Approximates the best fit for the points by minimizing the error \\
 \hline
 2 & Essentially, it forms a projection of the original points onto the new vector space & Predicts $y$ from $x$ through a function $f(x_1,x_2,....,x_n) = y$ \\
 \hline
 3 & Not used for predictions, as original feature space (\ie $x_1$ and $x_2$) give way to a new reduced dimension. Cordinates $x_1, x_2,...,x_n$ give way to $z_1,....,z_k$ where $k \leq n$ & \\[1ex]
 \hline
\end{tabular}
\caption{Table comparing PCA with Linear Regression.}
\label{table:pca_vs_linreg}
\end{table}
